\documentclass[11pt]{article}

\input{includes}

\begin{document}
\title{Facilities, Equipment and Other Resources}
\author{}
\date{}

\maketitle

The PIs, senior personnel, collaborators, and program trainees will access to a wide range of research computing and instruction facilities at the University of New Mexico.

UNM students and faculty on the projects will have access to advanced cyberinfrastructure 
resources through the UNM Center for Advanced Research Computing (CARC),
at which Prof.~Bridges is Director.
The UNM CARC supports high performance and data intensive computing by the entire UNM community. Resources available to support this project include the 280-node/2240-core Wheeler capacity compute cluster and the 32-node Xena NVIDIA GPU cluster. The systems are connected to a NetApp storage array which provides large-scale home directory storage to UNM users. This combination of significant compute capacity, modern accelerator-based computing, and large-scale storage provides a diverse set of systems for use by Ambassador trainees. These systems are housed in CARC's dedicated research data center with 2 UPS systems and 3 Liebert AC systems; together they provide 270 kVa of UPS capacity and 70 tons of dedicated cooling, maintaining a time window for riding out transient power loss or cleanly shutting down systems in the event of longer outages.

The UNM Department of Computer Science and Center for Advanced Research Computing also house multiple computer labs and workshop/teaching labs room for teaching computing classes and labs. These facilities include multiple rooms with 30+ networked Linux workstations, as well as telecommunication equipment for remote attendance and recording training sessions.

These and other UNM systems are connected across campus by multiple 10G connections, and UNM also hosts a dedicated 10G Science DMZ research network. Wide-area Internet connectivity to UNM includes 100G connections to the DOE Energy Sciences Network (ESNet) and the Western Regional Network, both through the Albuquerque Gigapop.

Finally, PI Bridges is an affiliate research scientist with the Chameleon NSFCloud Project, and UNM students and researchers also have access to large-scale systems through the NSF XSEDE program. In particular, multiple UNM staff members are XSEDE Campus Champions, and can support project participants in creating requests for startup, teaching, and research allocations on XSEDE systems. Each of these systems will be made available to project participants through teaching allocations if appropriate to the needs of student and class.

\end{document}
