\section{The New Mexico CUE Consortium}
\label{sec:consortium}


[ENRICO] We need to motivate here why the three institutions are the right combination for the consortium. Some ideas:
\begin{itemize}
    \item these are the only three research universities in the state
    \item share a common commitment to advance the diverse population of the state
    \item share a culture of inclusion and diversity in CS
    \item share a culture of interdisciplinary work (need examples)
\end{itemize}
... Because of this, the 
long-term problem we seek to address is: \emph{What research is needed to systematically 
quantify and optimize cyber-infrastructure performance tradeoffs?}

As motivating examples, consider... 


\subsection{Consortium's Institutions}

\paragraph{Overview of the University of New Mexico (UNM):}
% PGB to write here

\paragraph{Overview of New Mexico State University (NMSU):}
NMSU is the land-grant institution of New Mexico and one of the founding institutions of the Computing Alliance of Hispanic Serving Institutions (CAHSI). NMSU is the only Hispanic-serving land-grant institution in the continental US. Located in southern New Mexico, the institution serves a diverse student population---the local school districts have populations that are between 73\% and 98\% Hispanic, and include some of
the poorest counties in the US. NMSU is a Carnegie Doctoral University Higher Research Activity institution, with over \$100M in research expenditures, and it is a Carnegie Community Engagement University. NMSU offers 93 bachelor's degree programs, 56 master's degree programs and 27 doctoral programs. NMSU is ranked among top colleges by Forbes and US News \& World Report. CollegeNET places NMSU among the top 12\% for improving students’ social mobility. The Diverse: Issues in Higher Education places NMSU
in the top 10 institutions for bachelor’s degrees to Hispanic and Native American students. A study from USC places NMSU in the top 25 exemplar institutions for Hispanic STEM education.
In Fall 2018, NMSU had 14,289 students enrolled, of which 55.6\% were female, 56\% were Hispanic, 2.1\%
Native Americans, and 2.6\% African American. About 40\% of the students were Pell grant eligible.
NMSU offers both Bachelor of Arts and Bachelor of Science in Computer Science, as well as a newly established Bachelor of Science in Cybersecurity.  

\paragraph{Overview of New Mexico Tech (NMT):}

To be able to address these challenges, .. we need to be able to:
\begin{itemize}
\item I1
\item 
\item I3
\end{itemize}

Unfortunately, existing (approaches) are inadequate for these tasks. In particular, ...

\subsection{Consortium Organization}

[ENRICO] Specific roles for the different institutions? E.g., UNM lead/evaluation; NMSU lead criminal justice efforts; etc.