\section{Program Assessment and Evaluation}
\label{sec:assessment}
Program Assessment and Evaluation activities will be conducted by an internal evaluator with review by an external advisory board. As mentioned in the overview, the main metrics we are seeking to improve are the number of students applying for and admitted to NMIX+CS programs, NMIX+CS graduation and job placement rates, and the number and percentage of students from under-represented groups enrolled in and graduating from NMIX+CS programs, particularly women, Native American, and Hispanic students. 


To guide the development of an evaluation plan for the proposed research, we have developed the logic model shown in Table~\ref{tab:logic-model}. The model provides details of resources, activities, outputs, outcomes, and impact of the project.

\begin{table}[htb!]
\begin{tabular}{|p{1in}|p{1.35in}|p{1.2in}|p{1in}|p{1in}|}
    \hline
    \textbf{Resources}& \textbf{Activities}
    
   \textbf{(Outputs)} & \textbf{Short-term Outcomes} 
    & \textbf{Long-term Outcomes} &\textbf{Impact} \\
    \hline
    \textbf{UNM:}
    
    Department of Chemical and Biological Engineering
 
    \vspace{0.1in}
    Department of Sociology
    
     \vspace{0.25in}
     \textbf{NMSU:}
     
     Criminal Justice Department

     \vspace{0.1in}
     The School of Nursing
          
     \vspace{0.25in}
     \textbf{NMT:}

      Department of Business and Tech. Management
       
      \vspace{0.1in}
      Department of Psychology and Education 
    &
    Developing new courses (\# of developed courses, enrollment in  courses)

    \vspace{0.1in}
    Identifying and modifying existing relevant courses (\# of modified courses)

    \vspace{0.1in}
    Developing components on ethics to be integrated in current and new courses (\# of developed modules)
    
 \vspace{0.1in}
Student recruitment and support activities (\# of applications/ admissions)

 \vspace{0.1in}
Faculty and peer mentoring activities

 \vspace{0.1in}
NIC meetings, workshops, advisory group meetings, and discussions on best practices and evaluation results (\# of shared courses/modules).
    & 
    \textbf{Non-CS students:}

    Developing computing knowledge and skills 

    Increased self-efficacy and understanding of the subject matter

    \vspace{0.1in}
    \textbf{CS students:}
    
    Increased understanding of the broader impacts of CS

    \vspace{0.1in}
    \textbf{Institutions:}
    
    Broadened participation in computing disciplines (\# of students admitted to the program, \# of students from diverse backgrounds in program)
       
    \vspace{0.1in}
    \textbf{Non-CS departments:}
    
    Increased student knowledge of computational techniques 
    & 
    Increased non-CS graduates with computational knowledge and skills (NMIX+CS graduation rates) 
 
 \vspace{0.1in}
     Increased student interest in pursuing degrees/ careers which require computational skills and knowledge (\# of NMIX+CS graduates pursuing degrees/careers with computational technique) 

    \vspace{0.1in}
    Increased cooperation between CS and non-CS departments/faculty

    & 
    
    A diverse NM workforce with computational knowledge and skills (\# of under-represented NMIX+CS graduates in computing-related workforce)
    
    \vspace{0.1in}
    An integrated state-wide framework for
CS+X education programs 

    \\
    
    % This row is about NIC activities
%    Let’s put a row at the bottom to describe the elements related to the NIC—this will help address the solicitation requirements.
%    &
%    &
%    Activities of NIC (meetings, workshops, advisory group meetings)
%    &
%    Something about NIC across NM?
%    &
%    \\
\hline
\end{tabular}
\caption{Evaluation Plan Logic Model}
\label{tab:logic-model}
\end{table}

\subsection{Purpose}
The purpose of the proposed evaluation plan is to determine to what extent and in what ways the proposed program achieves its intended outcomes. The results will be used to improve the program to increase attainment of outcomes and sustainability. The following questions will guide the evaluation efforts: 
\begin{enumerate}
\item To what extent and in what ways does the program succeed in improving computational thinking among the students? 
\item To what extent and in what ways does the program succeed in increasing the capacity of faculty and programs to address computational thinking in non-CS disciplines? 
\item To what extent and in what ways does the program influence the career development of participants?
\item To what extent and in what ways does the program succeed in coordinating the efforts to develop an integrated state-wide framework for CS+X education programs?
\item What are the program impacts on development and diversity of next generation of individuals with computational thinking skills?
\end{enumerate}

\subsection{Methods}
A mix of qualitative and quantitative methods will be used for this evaluation. The goal is to understand the program and to determine the attainment of its short-term and long-term outcomes as well as making judgments about its impacts by using a combination of methods and approaches that are appropriate and relevant to the scope and the overall goals of the program.    

Considering the short timeline of the project, formative evaluation activities will be conducted in each semester in order to inform and modify programmatic activities in subsequent semesters. In addition, new data collection at the end of the 18 month period, along with the results from the formative evaluation, will be used to determine the overall success of the program (summative evaluation). 

\subsection{Data Collection Methods}
\begin{description}
\setlength\itemsep{0in}
\item[Data collection method 1:] The data from the course assignments: in partnership with the instructors at each institution, a sub set of course assignments will be selected to be analyzed in order to assess the students’ accomplishments as part of the course work. 
\item[Date collection method 2:] The program statistics such as enrollment data, participants’ grades, etc. 
\item[Data collection method 3:] The data from conducting a survey to understand student interests and goals for pursuing the certificate/ enrolling in the course: This questionnaire will include close-ended and open-ended questions to understand students’ perceptions of the program and the possible benefits and also their goals in pursuing the certificate (at the beginning of each semester). 
\item[Data collection method 4:] End of semester questionnaire: This questionnaire will include both closed and open-ended questions to gather students’ feedback regarding the program/ course and their progress. 
\item[Data collection method 5:] Interviews with the informants from the participating departments in each institution to understand their overall perception of the program and its strengths and weaknesses as perceived by the participating departments 
\item[Date collection method 6:] A focus group of students who completed the program in each institution (at the end of the 18 months period) 
\item[Data collection method 7:] Individual interviews with students/instructors/teaching assistants might be considered as needed for clarification of inconsistencies in data. 
\end{description}
Data analysis will include open coding for qualitative data (focus group and open-ended questions) as well as descriptive and simple inferential statistics for quantitative data.  

\subsection{External Advisory Board}
An External Advisory Board (EAB) will provide critical review of the project design and activities. The EAB will meet twice: once within the first six months of the beginning of the project (2020) and once within the last six months of the project (2021). EAB meetings will be in-person meetings with the option of virtual participation for those who are unable to travel. In order to maintain independence of the EAB, NM EPSCoR will act as the EAB convener and will structure the meeting agendas to include a review of curriculum development activities, organizational structure, mechanisms for and evidence of institutional collaborations, data collection, analyses, and reporting plans. EAB members will have the opportunity to substantively influence the project’s activities and improve the quality of findings. EAB members reflect the diversity of non-computer science disciplines represented by the project as well as computer science expertise.
%see Figure XXX.
%ssc if there is space, it would be nice to include a list of the EAB here. 
