\section{Implementation Plan}
Idea: half a page outlining a vision for the group would be good since it's not clear that NSF knows what theend result should look like.
%ssc I could develop a gantt chart that will show the timeframe for various activities based on the narrative below. 

\subsection{Educational Development}
Basically try to deploy the intro modules through the first two computing classes over 18 months.
\begin{description}
    \item[Spring 2020] Module development/deployment/assessment for discipline intro classes - 6 1 week course modules
    \item[Summer 2020] Evaluate/assess spring results, develop fall discipline/general course
    \begin{itemize}
        \item Discipline assignments in core classes?
        \item Sophomore-level data science class with discipline-specific project/modules?
        \item Develop student mentor trainings
    \end{itemize}
    \item[Fall 2020] Train mentors at start of semester. Continue development of data science class? Offer core class to discipline participants, Mentoring activities and assessment in the core class? Continue/refine modules
    \item[Spring 2021] Offer and assess data science class. Continue/refine modules
    \item[Summer 2021] Specialize data science class to specific disciplines as determined. Start to develop projects for use in capstone classes
\end{description}

\paragraph{NIC Collaboration}

\begin{description}
    \item[Spring 2020] Kickoff meeting at Sevilleta - finalize metrics, assessment, initial planning/coordination of module development, etc. Bi-weekly within institution, Monthly zoom meetings, slack channel for informal NIC communications
    \item[Summer 2020] 
    \begin{itemize}
        \item In-person project meeting + advisory board meeting
        \item Align CS core classes at institutions 
        \item Initial cross-institution course sharing discussions
    \end{itemize}
    \item[Fall 2020] Regular project meeting (discssions of assessment/metrics, etc.). Late fall programmatic assessment meeting
    \item[Spring 2021] Regular project meeting Mentor/trainee meetings?  Sustainability Plan???
    \item[Summer 2021] Programmatic assessment meeting
\end{description}

Budget ideas:
\begin{itemize}
    \item Faculty support (3 faculty months at NMSU/NMT, 4 at UNM with Amir as assessment/ethics lead) - \$60k at NMSU/NMT, \$80k at UNM
    \item Mentor support participant costs - 3/institution @ \$2500/semester \$22,500/institution
    \item Travel, assessment materials, advisory board travel/honoraria
    \item misc materials
\end{itemize}
